Global adjoint tomography -- Model GLAD-M25\footnote{This paper is dedicated to Dimitri Komatitsch, computational geophysicist extraordinaire, who passed away unexpectedly shortly before its submission.}

### 2019-01-29 main.tex
update phase histogram

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
  \caption{Histograms of 17--40~s P-wave traveltime anomalies of the vertical and radial components for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
  }
  \label{fig:P_phase_hist}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_360_P.pdf}
  \caption{Same as Fig.~\ref{fig:P_phase_hist}, except for the held-out database.}
  \label{fig:phase_hist_360_P}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_phase.pdf}
  \caption{Histograms of 17--40~s traveltime anomalies of P arrival(Vertical and Radial), and SH arrival(Transverse) for models S362ANI combined with CRUST2.0 (M00, Black), GLAD-M15 (M15, Green), and GLAD-M25 (M25, Red).
  }
  \label{fig:PS_phase_hist}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figures/dt_histogram_360_phase.pdf}
  \caption{Same as Fig.~\ref{fig:PS_phase_hist}, except for the held-out database.}
  \label{fig:phase_hist_360_P}
\end{figure}
